The helicoverpa package

### 2018-08-27 notebook/helicoverpa_notes.Rmd
Notebook update

>>>>

**Update to transferring to JSON**

    if(pest_move_dist > xdim & pest_move_dist > ydim){
        pest_move_dist <- max(c(xdim, ydim)); # Avoids error
    }
    # Start initialising the landscape and pests
    LAND <- toy_initialise_land(xdim  = xdim, ydim = ydim, 
                                pathogens = pathogens, crops = crops);
    PEST <- toy_initialise_pest(LAND, N = pest_init, p_al = path_alleles, 
                                c_al = crop_alleles);
    # Start the generations
    PEST_DATA   <- NULL;
    LAND_DATA   <- NULL;
    gen         <- 1;
    while(gen < generations){
        LAND <- toy_set_crops(LAND, crops, crop_rotate);                        
        LAND <- toy_set_paths(LAND, pathogens, path_rotate);                    
        PEST <- toy_move_pest(PEST, LAND, pest_move_pr, pest_move_dist);        
        PEST <- toy_feed_pest(PEST, LAND);                                      
        if(toy_check_extinction(PEST, gen) == TRUE){ # Hate these if breaks here
            break;
        }
        PEST <- toy_kill_pest(PEST, LAND);
        if(toy_check_extinction(PEST, gen) == TRUE){
            break;
        }
        PEST <- toy_reproduce_pest(PEST, LAND, path_alleles, crop_alleles, 
                                   fecundity, cell_K);
        if(toy_check_extinction(PEST, gen) == TRUE){
            break;
        }
        PEST_DATA[[gen]] <- PEST;
        LAND_DATA[[gen]] <- LAND;
        gen <- gen + 1;
    }
    return(list(PEST_DATA = PEST_DATA, LAND_DATA = LAND_DATA));
}

results_to_json <- function(pest, land, printit = TRUE, filename = "sim.json"){
    if("package:jsonlite" %in% search() == FALSE){
        stop("Error: Need to load the R package 'jsonlite'")
    }
    inds   <- dim(pest)[1];
    p_geno <- rep(x = 0, times = inds);
    c_geno <- rep(x = 0, times = inds);
    path   <- rep(x = 0, times = inds);
    crop   <- rep(x = 0, times = inds);
    r_path <- rep(x = 0, times = inds);
    r_crop <- rep(x = 0, times = inds);
    for(i in 1:inds){ # Doing this a bit lazily, without refactoring the rest
        p_geno[i] <- as.numeric( paste(pest[i,5], pest[i,6], sep = ""));
        c_geno[i] <- as.numeric( paste(pest[i,7], pest[i,8], sep = ""));
        xloc      <- pest[i, 3];
        yloc      <- pest[i, 4];
        path[i]   <- land[xloc, yloc, 2];
        crop[i]   <- land[xloc, yloc, 3];
        if(pest[i,5] == path[i] | pest[i,5] == path[i]){
            r_path <- 1;
        }
        if(pest[i,7] == crop[i] | pest[i,8] == crop[i]){
            r_crop <- 1;
        }
    }
    data      <- matrix(data = 0, nrow = inds, ncol = 10);
    data[,1]  <- pest[,1];
    data[,2]  <- pest[,2];
    data[,3]  <- pest[,3];
    data[,4]  <- pest[,4];
    data[,5]  <- path;
    data[,6]  <- crop;
    data[,7]  <- p_geno;
    data[,8]  <- c_geno;
    data[,9]  <- r_path;
    data[,10] <- r_crop;
    colnames(data) <- c("ID", "sex", "xloc", "yloc", "path", "crop", 
                        "p_geno", "c_geno", "resist_path", "eat_crop");
    modsim <- list( traits = colnames(data), 
                    values = unname(apply(data, 1, 
                                          function(x) as.data.frame(t(x))))
    );
    sim_json <- toJSON(list(traits = names(modsim), values = modsim), 
                       pretty = TRUE);
    if(printit == TRUE){
        write(sim_json, filename);
    }
    return(sim_json);
}

The function below has now been modified, along with the outer function for simulating resistance.

```{r}
toy_simulate_resistance <- function(generations = 20,       # Generations to sim
                                    xdim = 2,               # Land dimension 1
                                    ydim = 2,               # Land dimension 2
                                    pathogens = 1,          # Pathogen strains
                                    crops = 1,              # Crop species
                                    path_alleles = 3,       # Pathogen alleles
                                    crop_alleles = 3,       # Crop alleles
                                    pest_init = 2000,       # Initial pests 
                                    crop_rotate = "static", # Crops rotated
                                    path_rotate = "static", # Pathogens rotated
                                    pest_move_pr = 0.1,     # Pest movement
                                    pest_move_dist = 1,     # Pest move distance
                                    fecundity = 8,          # Offspring per fem
                                    cell_K = 2000           # K per cell
                                    ){

    if(pest_move_dist > xdim & pest_move_dist > ydim){
        pest_move_dist <- max(c(xdim, ydim)); # Avoids error
    }
    # Start initialising the landscape and pests
    LAND <- toy_initialise_land(xdim  = xdim, ydim = ydim, 
                                pathogens = pathogens, crops = crops);
    PEST <- toy_initialise_pest(LAND, N = pest_init, p_al = path_alleles, 
                                c_al = crop_alleles);
    # Start the generations
    PEST_DATA   <- NULL;
    LAND_DATA   <- NULL;
    gen         <- 1;
    while(gen < generations){
        LAND <- toy_set_crops(LAND, crops, crop_rotate);                        
        LAND <- toy_set_paths(LAND, pathogens, path_rotate);                    
        PEST <- toy_move_pest(PEST, LAND, pest_move_pr, pest_move_dist);        
        PEST <- toy_feed_pest(PEST, LAND);                                      
        if(toy_check_extinction(PEST, gen) == TRUE){ # Hate these if breaks here
            break;
        }
        PEST <- toy_kill_pest(PEST, LAND);
        if(toy_check_extinction(PEST, gen) == TRUE){
            break;
        }
        PEST <- toy_reproduce_pest(PEST, LAND, path_alleles, crop_alleles, 
                                   fecundity, cell_K);
        if(toy_check_extinction(PEST, gen) == TRUE){
            break;
        }
        PEST_DATA[[gen]] <- PEST;
        LAND_DATA[[gen]] <- LAND;
        gen <- gen + 1;
    }
    return(list(PEST_DATA = PEST_DATA, LAND_DATA = LAND_DATA));
}

results_to_json <- function(pest, land, printit = TRUE, filename = "sim.json"){
    if("package:jsonlite" %in% search() == FALSE){
        stop("Error: Need to load the R package 'jsonlite'")
    }
    inds   <- dim(pest)[1];
    p_geno <- rep(x = 0, times = inds);
    c_geno <- rep(x = 0, times = inds);
    path   <- rep(x = 0, times = inds);
    crop   <- rep(x = 0, times = inds);
    r_path <- rep(x = 0, times = inds);
    r_crop <- rep(x = 0, times = inds);
    for(i in 1:inds){ # Doing this a bit lazily, without refactoring the rest
        p_geno[i] <- as.numeric( paste(pest[i,5], pest[i,6], sep = ""));
        c_geno[i] <- as.numeric( paste(pest[i,7], pest[i,8], sep = ""));
        xloc      <- pest[i, 3];
        yloc      <- pest[i, 4];
        path[i]   <- land[xloc, yloc, 2];
        crop[i]   <- land[xloc, yloc, 3];
        if(pest[i,5] == path[i] | pest[i,5] == path[i]){
            r_path <- 1;
        }
        if(pest[i,7] == crop[i] | pest[i,8] == crop[i]){
            r_crop <- 1;
        }
    }
    data      <- matrix(data = 0, nrow = inds, ncol = 10);
    data[,1]  <- pest[,1];
    data[,2]  <- pest[,2];
    data[,3]  <- pest[,3];
    data[,4]  <- pest[,4];
    data[,5]  <- path;
    data[,6]  <- crop;
    data[,7]  <- p_geno;
    data[,8]  <- c_geno;
    data[,9]  <- r_path;
    data[,10] <- r_crop;
    colnames(data) <- c("ID", "sex", "xloc", "yloc", "path", "crop", 
                        "p_geno", "c_geno", "resist_path", "eat_crop");
    modsim <- list( traits = colnames(data), 
                    values = unname(apply(data, 1, 
                                          function(x) as.data.frame(t(x))))
    );
    sim_json <- toJSON(list(traits = names(modsim), values = modsim), 
                       pretty = TRUE);
    if(printit == TRUE){
        write(sim_json, filename);
    }
    return(sim_json);
}
```

We can run things the same way to generate the output. Note that the output from `toy_simulate_resistance` has changed, so now we need to read the list into `results_to_json`. The list contains the elements `PEST_DATA` and `LAND_DATA`.

```{r}
library(jsonlite);
sim  <- toy_simulate_resistance(pathogens = 3, crops = 3);
json <- results_to_json(pest = sim$PEST_DATA[[19]], land = sim$LAND_DATA[[19]],
                        filename = "../data/sample_sim.json");
```

 The output is [here]([sample_sim.json](https://github.com/bradduthie/helicoverpa/blob/dev/data/sample_sim.json)).
